---
title: "R Notebook"
output:
  html_document:
    toc: true
    toc_float:
      copllapsed: true
    df_print: paged
    toc_depth: 4
    theme: flatly
    code_folding: hide
  html_notebook:
    code_folding: hide
editor_options:
  chunk_output_type: console
---

```{r}
library("pacman")
library("pacman")
pacman::p_load(
  modelsummary,
  summarytools,
  glue,
  purrr,
  sjPlot,
  sjmisc,
  car,
  ggeffects,
  here,
  haven,
  pwr, # Power analysis
  stats,
  rlang,
  janitor,
  ggplot2,
  dplyr,
  ggthemes,
  margins,
  estimatr,
  tidyverse,
  broom,
  lmtest,
  htmltools,
  gridExtra,
  scales,
  rio,
  stringr,
  readxl,
  kableExtra,
  magick,
  labelled,
  leaflet
)

# Set theme
theme_set(theme_bw())
theme_update(
  panel.border = element_rect(fill = NA),
  panel.background = element_rect(fill = "white"),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  strip.background = element_rect(fill = "gray90"),
             strip.text.y = element_text( size = 10)) # Attrubute text size)

# CREATE NO_ZERO FUNCTION FOR GGPLOT

no_zero <- function(x) {
  y <- sprintf('%.1f',x)
  y[x > 0 & x < 1] <- sprintf('.%s',x[x > 0 & x < 1]*10)
  y[x == 0] <- '0'
  y[x > -1 & x < 0] <- sprintf('-.%s',x[x > -1 & x < 0]*-10)
  y
}


options(scipen=999) # Get's rid of scientific notation of high numbers

```

# Data wrangling
```{r}
dfraw <- import(here::here("0_raw_data", "data.dta"))

df <- dfraw

# Recoding the first. Notice that there is an output error in the original data
# The relevant items is Q34-Q37 in the word dokument. The problem is that Q34_1,_2,_3,_4 comes out as  Q36_1,_2,_4,_3. Because it does so the order is non-logical on both number and order. Thus, the "real" Q36s is named v74-v77 in the data file - and they are also named as Q36 in the word document.


#Q34 er Q36: I'm so sick of ${e://Field/group}. They are a bunch of idiots who are tearing our country apart!  
#Q35 er Q35: I've had enough of ${e://Field/group}. If you ask me, they are worthless pigs! 
#Q36 er v74-v77: There is a certain similarity between vermin and ${e://Field/group}. Let’s exterminate both! 
#Q37 er Q37: I just started collecting names of ${e://Field/group}. Those kinds of people deserve a bullet to the head! 


df <- dfraw %>%
  rename(resid = respondentid,
         attention_check = q32) %>% 
  select(everything(), -c("distributionchannel", "userlanguage", "country", "resp", "tasktootherproject_do", "rid", "recordeddate", "progress", "staus","enddate",
                          "q17_1","q17_2",
                          "q18_1","q18_2",
                          "q19_1","q19_2",
                          "q20_1","q20_2",
                          "q21_1","q21_2",
                          "q22_1","q22_2",
                          "q23_1","q23_2",
                          "q24_1","q24_2",
                          "q25_1","q25_2",
                          "q26_1","q26_2",
                          "q27_1","q27_2",
                          "q28_1","q28_2",
                          "q29_1","q29_2",
                          "q30_1","q30_2",
                          "q31_1","q31_2"),
         -starts_with(c("fl_", "gender_", "party_", "dem_", "stat_","age_"))) %>% 
  mutate(across(
    c("q36_1", "q35_1", "v74", "q37_1"),
    ~ case_when(
      .x == "Extremely unlikely" ~ 1,
      # "Extremely unlikely",
      .x == "Very unlikely"  ~ 2,
      # "Very unlikely",
      .x == "Somewhat unlikely" ~ 3,
      # "Somewhat unlikely",
      .x == "Neither likely nor unlikely" ~ 4,
      # "Neither likely nor unlikely",
      .x == "Somewhat likely" ~ 5,
      # "Somewhat likely",
      .x == "Very likely" ~ 6,
      #"Very likely",
      .x == "Extremely likely" ~ 7,
      # "Extremely likely"
    )
  )) %>%
  dplyr::rename(
    occur_1 = q36_1,
    occur_2 = q35_1,
    occur_3 = v74,
    occur_4 = q37_1
  ) %>%
  mutate(across(
    c("q36_2", "q35_2", "v75", "q37_2"),
    ~ case_when(
      .x == "Extremely unlikely" ~ 1,
      # "Extremely unlikely",
      .x == "Very unlikely"  ~ 2,
      # "Very unlikely",
      .x == "Somewhat unlikely" ~ 3,
      # "Somewhat unlikely",
      .x == "Neither likely nor unlikely" ~ 4,
      # "Neither likely nor unlikely",
      .x == "Somewhat likely" ~ 5,
      # "Somewhat likely",
      .x == "Very likely" ~ 6,
      #"Very likely",
      .x == "Extremely likely" ~ 7,
      # "Extremely likely"
    )
  )) %>%
  dplyr::rename(
    trigger_1 = q36_2,
    trigger_2 = q35_2,
    trigger_3 = v75,
    trigger_4 = q37_2
  ) %>%
  mutate(across(
    c("q36_4", "q35_4", "v77", "q37_4"),
    # NOTE HERE THAT IT IS Q36_4 instead of Q36_3 etc - SEE KRISTIANS MAIL 21-01-22
    ~ case_when(
      .x == "Extremely unlikely" ~ 1,
      # "Extremely unlikely",
      .x == "Very unlikely"  ~ 2,
      # "Very unlikely",
      .x == "Somewhat unlikely" ~ 3,
      # "Somewhat unlikely",
      .x == "Neither likely nor unlikely" ~ 4,
      # "Neither likely nor unlikely",
      .x == "Somewhat likely" ~ 5,
      # "Somewhat likely",
      .x == "Very likely" ~ 6,
      #"Very likely",
      .x == "Extremely likely" ~ 7,
      # "Extremely likely"
    )
  )) %>%
  dplyr::rename(
    offend_1 = q36_4,
    offend_2 = q35_4,
    offend_3 = v77,
    offend_4 = q37_4
  ) %>%
  mutate(across(
    c("q36_3", "q35_3", "v76", "q37_3"),
    # NOTE HERE THAT IT IS Q36_4 instead of Q36_3 etc - SEE KRISTIANS MAIL 21-01-22
    ~ case_when(
      .x == "Extremely unlikely" ~ 1,
      # "Extremely unlikely",
      .x == "Very unlikely"  ~ 2,
      # "Very unlikely",
      .x == "Somewhat unlikely" ~ 3,
      # "Somewhat unlikely",
      .x == "Neither likely nor unlikely" ~ 4,
      # "Neither likely nor unlikely",
      .x == "Somewhat likely" ~ 5,
      # "Somewhat likely",
      .x == "Very likely" ~ 6,
      #"Very likely",
      .x == "Extremely likely" ~ 7,
      # "Extremely likely"
    )
  )) %>%
  dplyr::rename(
    tensions_1 = q36_3,
    tensions_2 = q35_3,
    tensions_3 = v76,
    tensions_4 = q37_3
  ) %>%
  mutate(republican = as.factor(
    case_when(q14 == "Democratic Party" ~ 0,
              q14 == "Republican Party" ~ 1)
  ),
  treatment = factor(
    group,
    levels = c(
              "Democrats", 
              "Republicans",
              "black people",
              "white people",
              "Muslims",
              "Christians"),
    labels = c(
              "Democrats", 
              "Republicans",
              "Black people",
              "White people",
              "Muslims",
              "Christians"))) %>% 
  # RESHAPE
  pivot_longer(
    cols = c(
      starts_with("occur_"),
      starts_with("tensions_"),
      starts_with("trigger_"),
      starts_with("offend_")
    ),
    names_to = c(".value", "task"),
    # ".value" pivot_longer() that that part of the column name specifies the “value” being measured (which will become a variable in the output)
    names_sep = "_",
    values_drop_na = FALSE
  ) %>%
  mutate(across(c("occur","offend", "tensions", "trigger"),
                 ~rescale(.x))) %>% 
  dplyr::select(resid, treatment, task, occur, offend, tensions, trigger, everything())


save(df, file = here::here("1_recoded_data", "infer_harm_data.Rdata"))


```

## Calculate means 
```{r}
df %>% group_by(resid, treatment) %>% 
  summarise_at(c("occur", "offend", "tensions", "trigger"), mean, na.rm = TRUE) %>% 
  filter(!is.na(offend))
```

# Analysis

## Outcomes <-- treatment
### Do people perceive a higher prevalence of hostile statements based on who it is targeting?

ETHNIC AND RELIGIOUS GROUPS VS POLITICAL GROUPS

- H1a: Statements targeting ethnic (white/black people) and religious (Muslims/Christians)are perceived to be more likely to occur on social media, compared to statements targeting political groups (Democrats and Republicans): **Not supported. If anything statements targeting political groups are more prevalent**

MINORITY VS MAJORITY

- H1b: Statements targeting minority groups (Muslims and black people) are perceived to be more likely to occur on social media, compared to statements targeting majority groups ( Christians and white people): **Not supported**

### Do people infer more harm when hostile statements are targeting specific groups?

ETHNIC AND RELIGIOUS GROUPS VS POLITICAL GROUPS

- H2a: Statements targeting ethnic (white/black people) and religious (Muslims/Christians) are perceived to be more likely to 1) trigger riots or physical violence 2) offend a lot of people, and 3) increase tensions between groups in society than statements targeting political groups (Democrats and Republicans)
  + Offends a lot of people: Support compared to democrats
  + Increases group tensions: Support compared to democrats
  + Triggers riots or violence: Suport compared to Democrats and Republicans

MINORITY VS MAJORITY

- H2b: Statements targeting minority groups (Muslims and black people) are perceived to be more likely to 1) trigger riots or physical violence 2) offend a lot of people, and 3) increase tentions between groups in society, compared to statements targeting majority groups ( Christians and white people)
  + Support compared to Christians


```{r, fig.height=4}
load(here::here("1_recoded_data" , "infer_harm_data.Rdata"))

# Define vars
dvs <- c("occur", "offend", "tensions", "trigger")
ivs <-  c("treatment")

# Specificy formulas
fs <- crossing(dvs, ivs)  %>%
  mutate(f = glue("{dvs} ~ {ivs}"))

# Apply lm function on formulas, create tidy dataframe 3) filter relevant coefficients
m <- fs %>%
  mutate(model = map(f, ~ lm_robust(
    formula = as.formula(.x),
    data = df,
    clusters = resid
  ))) %>%
  mutate(tidy_model = map(model, broom::tidy)) %>%
  unnest(tidy_model) %>% 
  filter(term != "(Intercept)") %>% 
  mutate(term = factor(
    term,
    levels = c(
      "treatmentBlack people",
      "treatmentWhite people",
      "treatmentMuslims",
      "treatmentChristians",
      "treatmentRepublicans"
    ),
    labels = c("Black people",
               "White people",
               "Muslims",
               "Christians",
               "Republicans"
    )), 
    outcome = factor(
      outcome,
      levels = c("occur",
                 "offend",
                 "tensions",
                 "trigger"),
      labels = c("Occurs on SoMe",
                 "Offends a lot of people",
                 "Increases group tensions",
                 "Triggers riots or violence")))


# Create plot
m %>%
  ggplot(aes(x = estimate,
             y = term)) +
  facet_wrap( ~ outcome, ncol = 4) +
  geom_vline(xintercept = 0) +
  geom_point(aes(),
             colour = ifelse(m$conf.low > 0 |
                               m$conf.high < 0, "black", "gray49")) +
  geom_errorbarh(
    aes(xmin = conf.low, xmax = conf.high),
    height = 0,
    linetype = ifelse(m$conf.low > 0 |
                        m$conf.high < 0, "solid", "dashed"),
    colour = ifelse(m$conf.low > 0 |
                      m$conf.high < 0, "black", "gray49")
  ) +
  scale_x_continuous(
    limits = c(-.2,.2)
  ) +
  labs(
    x = "",
    y = "",
    title = "",
    subtitle = "",
    caption = ""
  )

```
## Outcome <-- treatment * partisanship
```{r}
load(here::here("1_recoded_data" , "infer_harm_data.Rdata"))

# Define vars
dvs <- c("occur", "offend", "tensions", "trigger")
ivs <-  c("treatment")
ins <- c("republican")

# Specificy formulas
fs <- crossing(dvs, ivs, ins)  %>%
  mutate(
    f = glue("{dvs} ~ {ivs} * {ins}"))

# Apply lm function on formulas, create tidy dataframe 3) filter relevant coefficients
models <- fs %>%
  mutate(model = map(f, ~ lm_robust(
    formula = as.formula(.x),
    data = df,
    clusters = resid
  ))) 

# Predict the the model. Column 6, row 1 (of 18 )
m1 <- ggpredict(models[[5]][[1]], terms = c("treatment", "republican")) %>% 
  mutate(model = "occur")

m2 <- ggpredict(models[[5]][[2]], terms = c("treatment", "republican")) %>% 
  mutate(model = "offend")

m3 <- ggpredict(models[[5]][[3]], terms = c("treatment", "republican")) %>% 
  mutate(model = "tensions")

m4 <- ggpredict(models[[5]][[4]], terms = c("treatment", "republican")) %>% 
  mutate(model = "trigger")

    
m <- bind_rows(m1, m2,m3,m4) %>% 
  mutate(Republican = group)


ggplot(m, aes(x = predicted, # Level for x variable
              y = x, # Predicted value at level
              color = Republican))+
  facet_wrap(~model, ncol = 2)+ # What group
  geom_point(position =position_dodge(width= 0.5))+

  geom_errorbarh(aes(xmin = m$conf.low, xmax = m$conf.high), position = position_dodge(width = 0.5), height = 0)+
  scale_x_continuous(limits = c(0,1))+
  labs(title = "",
       subtitle = "",
       y = "",
       x = "")


```


```{r}
knitr::knit_exit()
```
# Knit exit

## Old 

```{r}

 df %>% 
  select(starts_with("occur_"), starts_with("trigger_"),starts_with("offend_"), starts_with("tensions_"), treatment, republican) %>% 
  View()


#
fit1 <- lm(occur_1 ~ treatment*repbulican, data =df)
fit2 <- lm(occur_2 ~ treatment*repbulican, data =df)
fit3 <- lm(occur_3 ~ treatment*repbulican, data =df)
fit4 <- lm(occur_4 ~ treatment*repbulican, data =df)

plot_model(fit1, type = "int")
plot_model(fit2, type = "int")
plot_model(fit3, type = "int")
plot_model(fit4, type = "int")

fit1 <- lm(trigger_1 ~ treatment, data =df)
fit2 <- lm(trigger_2 ~ treatment, data =df)
fit3 <- lm(trigger_3 ~ treatment, data =df)
fit4 <- lm(trigger_4 ~ treatment, data =df)

plot_models(fit1, fit2, fit3, fit4)

fit1 <- lm(offend_1 ~ treatment, data =df)
fit2 <- lm(offend_2 ~ treatment, data =df)
fit3 <- lm(offend_3 ~ treatment, data =df)
fit4 <- lm(offend_4 ~ treatment, data =df)

plot_models(fit1, fit2, fit3, fit4)

fit1 <- lm(tensions_1 ~ treatment, data =df)
fit2 <- lm(tensions_2 ~ treatment, data =df)
fit3 <- lm(tensions_3 ~ treatment, data =df)
fit4 <- lm(tensions_4 ~ treatment, data =df)

plot_models(fit1, fit2, fit3, fit4)



fit <- lm(occur_1 ~ treatment, data =df)
plot_model(fit)


  pivot_wider(
    id_cols = c(
      resid, party_id7)
    ) %>% 
  count(party_id7) # Create new dataframe



models <- list(
  "occur" = lm(occur_1 ~ treatment,
                data = df))

modelsummary(
  models)

```

